---
title: "amazon_review_Sentiment_analysis_for_smart_watch_Fitbit"
author: "Deepak_Prakash"
date: "12/27/2021"
output: html_document

Mode1 :  
NLP Mode1 based on sentiment analysis in R 
Data : 
Amazon Product reviews
Output :
Sentiment score based on reviews 

```{r}
#Importing file into R

#Load packages into R 

install.packages("tm")
install.packages("wordcloud")
install.packages("syuzhet")

library(tm)          #For text analytics - text mining 
library(wordcloud)   #to create wordcloud 
library(syuzhet)

```
#Using packages (tm), (worldcloud), (syuzhet) for text mining and data cleaning
```{r}
#import data into R
reviews < - read.csv(file.choose(), header = T)
```
```{r}
#check the structure of file 
str(reviews)
```
#creating corpus 
#this funtion uses the base package funtion iconv to translate value labels
```{r}
corpus <- iconv(reviews$text)
corpus <- Corpus(VectorSource(corpus))
```
```{r}
#To See the corpus 

inspect(corpus[1:5] )
```
#cleaning Corpus
```{r}
corpus <- tm_map(corpus, tolower)

corpus <- tm_map(corpus, removePunctuation)

corpus <- tm_map(corpus, removeNumbers)

corpus <- tm_map(corpus, removeWords, stopwords("english"))

corpus <- tm_map(corpus, stripWhitespace)
```
#remove some common words not to used in text analysis - replace word 1, word 2 by actual words
```{r}
corpus <- tm_map(corpus, removeWords, c("watch", "build",  "battery", "price", "will", "get", "battery", "series", "display", "watch", "just", "days", "smart", "got","loaded","using" ))

reviews_final <- corpus
```

#create Term Document 
```{r}
tdm <- TermDocumentMatrix(reviews_final)
tdm <- as.matrix(tdm)
tdm[1:10, 1:5]

```
#Bar plot of words 
```{r}
w <- rowSums(tdm)
w<- subset(w, w>=25)
barplot(w, las = 2, col = "blue")

```
#create word cloud 
```{r}
w <- sort(rowSums(tdm), decreasing = T) 
set.seed(2000)
wordcloud(words = names(w), freq = w, max.words = 50, random.order = T, min.freq = 5, colors = brewer.pal(25, "Dark2"), scale = c(3,0.3))

```
# To obtain sentiment scores

```{r}
sentiment_data <- iconv(reviews$text)
s <- get_nrc_sentiment(sentiment_data)
s[1:10,]
```
#calculate review wise score 
```{r}
s$score <- s$positive - s$negative
s[1:10]
```
```{r}
write.csv(x = s, file = "/cloud/project/Sentiment_analysis/Final_score.csv")
```
#check product sentiment 

#check overall sentiment of the product
```{r}
review_score <- colSums(s[,])
print(review_score)
```
#Plot product sentiment 
#To Bar plot
```{r}
barplot(colSums(s), las = 2, col = rainbow(10), ylab = 'count', main ='sentiment')
```
